---
title: "p8105_hw3_wb2366"
auther: Wenhan Bao
Date: 2021-10-18
output: github_document
---

```{r}
library(tidyverse)
library(ggplot2)
```


## Problem1

**Load the data**
```{r load the data}
library(p8105.datasets)
data("instacart")
```

**How many aisles are there, and which aisles are the most items ordered from?**
```{r aisle}
aisle_df = count(instacart, aisle) %>%
  arrange(desc(n))
```

**Answer:** According to the result of the chunk above, there are **134** different aisles while **fresh vegetables** are the most items ordered from.

**Make a plot that shows the number of items ordered in each aisle, limiting this to aisles with more than 10000 items ordered. Arrange aisles sensibly, and organize your plot so others can read it.**
```{r make a plot, fig.width = 7}
filter(aisle_df, n > 10000) %>%
  mutate(aisle = fct_reorder(aisle, n)) %>%
  ggplot(aes(x = aisle, y = n)) +
    geom_col(width = .7,
             position = position_dodge(width = 0.9)) +
    labs(title = "The number of items ordered in each aisle",
         x = "Aisle",
         y = "The number of items") +
    theme(plot.title = element_text(hjust = 0.5, size = 15),
          axis.title.x = element_text(size = 12),
          axis.title.y = element_text(size = 12),
          axis.text.y = element_text(size = 8)) +
    coord_flip()
```

**Make a table showing the three most popular items in each of the aisles “baking ingredients”, “dog food care”, and “packaged vegetables fruits”. Include the number of times each item is ordered in your table.**
```{r Three most popular items}
popular_bak_df = filter(instacart, aisle == "baking ingredients") %>%
  select(aisle, product_name) %>%
  group_by(aisle, product_name) %>%
  tally() %>%
  arrange(desc(n)) %>%
  head(3)

popular_dog_df = filter(instacart, aisle == "dog food care") %>%
  select(aisle, product_name) %>%
  group_by(aisle, product_name) %>%
  tally() %>%
  arrange(desc(n)) %>%
  head(3)

popular_pack_df = filter(instacart, aisle == "packaged vegetables fruits") %>%
  select(aisle, product_name) %>%
  group_by(aisle, product_name) %>%
  tally() %>%
  arrange(desc(n)) %>%
  head(3)

popular_item_df = rbind(popular_pack_df, popular_bak_df, popular_dog_df)

knitr::kable(popular_item_df,
             caption = "The three most popular items in each of the aisles")
```

**Make a table showing the mean hour of the day at which Pink Lady Apples and Coffee Ice Cream are ordered on each day of the week; format this table for human readers (i.e. produce a 2 x 7 table).**
```{r the mean}
Pink_df = filter(instacart, product_name == "Pink Lady Apple") %>%
  mutate(mean_order_hour_of_day = round(mean(order_hour_of_day), digits = 2)) %>%
  select(product_name, aisle, department, mean_order_hour_of_day) %>%
  distinct()

Coffee_df = filter(instacart, product_name == "Coffee Ice Cream") %>%
  mutate(mean_order_hour_of_day = round(mean(order_hour_of_day), digits = 2)) %>%
  select(product_name, aisle, department, mean_order_hour_of_day) %>%
  distinct()

meanhour_df = rbind(Pink_df, Coffee_df)

knitr::kable(meanhour_df,
             caption = "The mean hour of the day at which Pink Lady Apples and Coffee Ice Cream are ordered")
```






